#~~~~~~~~~~~~~~~~~~~~~~~~~~# Data Preperation #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#

#install.packages("dplyr")
```{r}
library(plyr)
library(dplyr)
```

# Import file into R as dataframe
```{r}
credit_profiles <- data.frame(read.csv("german_credit.csv"), stringsAsFactors = FALSE)
```

# View dataframe and summary

```{r}
credit_profiles
summary(credit_profiles)
```

# Make new working data frame
```{r}
gcc <- credit_profiles
```

# Get classes for all data
```{r}
sapply(gcc, class)
```

# Make a subset of Numeric attributes
```{r}
numeric_subset<-subset.data.frame(germancredit, select=c("Duration.of.Credit..month.", "Credit.Amount", "Age..years.", "No.of.Credits.at.this.Bank"))
```

# For numeric columns, determine max, min and sd
```{r}
summary(numeric_subset)
apply(numeric_subset, 2, sd)

```

# Check for duplicates and NAs
```{r}
table(is.na(gcc))
anyDuplicated.data.frame(gcc)
```


# Assess Normality
```{r}
apply(numeric_subset, 2, shapiro.test)
```

# Find Range of Numeric Values
```{r}
range(gcc$Age..years.)
range(gcc$Duration.of.Credit..month.)
range(gcc$Credit.Amount)
range(gcc$No.of.Credits.at.this.Bank)
```

# Bin Numeric Values
```{r}
gcc$Duration.of.Credit..month. <-  cut(gcc$Duration.of.Credit..month., breaks = 7, labels = c("0-6 Months","7-12 Months","13-18 Months","19-24 Months","25-30 Months","31-36 Months", "37-42 Months"))
```


# Run For loop to bin Credit Amount and Age
```{r}
ca <- gcc$Credit.Amount
i <- 1
a <- list()
for (x in ca){
  if(x <= 5000) {(x = "<= 5000")}
  else if (x <=10000) {(x = "<= 10000")}
  else if (x >10000) {(x = "> 10000")}
  else if (x < 0) {(x= "Error")}
  else {"Please enter numeric value"}
  a[[i]] <- x
  i = i + 1
}
gcc$Credit.Amount <- replace(gcc$Credit.Amount, 1:1000, a)
gcc <- transform(gcc,Credit.Amount=unlist(Credit.Amount))
gcc$Credit.Amount <- as.factor(gcc$Credit.Amount)

```

# For Age
```{r}
ag <- gcc$Age..years.
i <- 1
age <- list()
for (x in ag){
  if(x <=25 ) {(x = "19-25")}
  else if (x <=50) {(x = "26-50")}
  else if (x <=75) {(x = "51-75")}
  else if (x > 75) {(x= "75+")}
  else if (x < 19) {(x = "Bad")}
  else {"Please enter numeric value"}
  age[[i]] <- x
  i = i + 1
}

gcc$Age..years. <- replace(gcc$Age..years., 1:1000, age)
gcc <- transform(gcc,Age..years.=unlist(Age..years.))
gcc$Age..years. <- as.factor(gcc$Age..years.)
```


# Add labels for data clarification.

```{r}
gcc$Creditability <- as.factor(gcc$Creditability)
gcc$Creditability <- revalue(gcc$Creditability, c("1" = "Good", "0" = "Bad"))

gcc$Account.Balance <- as.factor(gcc$Account.Balance)
gcc$Account.Balance <- revalue(gcc$Account.Balance, c("1" = "<0", "2" = "0-200", "3" = "<200", "4" = "No_Checking_Account"))

gcc$Payment.Status.of.Previous.Credit <- as.factor(gcc$Payment.Status.of.Previous.Credit)
gcc$Payment.Status.of.Previous.Credit <- revalue(gcc$Payment.Status.of.Previous.Credit, c("0" = "No Credit Taken", "1" = "All Paid", "2" = "Existing Paid", "3" = "Delayed Payment", "4" = "Critical Account"))

gcc$Purpose <- as.factor(gcc$Purpose)
gcc$Purpose <- revalue(gcc$Purpose, c("0" = "New Car", "1" = "Used car", "2" = "Furniture/Equipment", "3" = "Radio/TV", "4" = "Domestic Appliances", "5" = "Repairs", "6" = "Education", "7" = "Vacation", "8" = "Retraining", "9" = "Business", "10" = "Others"))

gcc$Value.Savings.Stocks <- as.factor(gcc$Value.Savings.Stocks)
gcc$Value.Savings.Stocks <- revalue(gcc$Value.Savings.Stocks, c("1"= "<100", "2" = "100-500", "3" = "500-1000", "4" = "> 1000", "5" = "Unknown/No Savings Account "))

gcc$Length.of.current.employment <- as.factor(gcc$Length.of.current.employment)
gcc$Length.of.current.employment <- revalue(gcc$Length.of.current.employment, c("1" = "Unemployed", "2" = "< 1 year", "3" = "1 - 4 years", "4" = "4 - 7 years", "5" = "> 7 years"))

gcc$Sex...Marital.Status <- as.factor(gcc$Sex...Marital.Status)
gcc$Sex...Marital.Status <- revalue(gcc$Sex...Marital.Status, c("1" = "Male_Divorced/Seperated", "2" = "Female_Divorced/Seperated/Married", "3" = "Male_Single", "4" = "Male_Married/Widowed"))

gcc$Guarantors <- as.factor(gcc$Guarantors)
gcc$Guarantors <- revalue(gcc$Guarantors, c("1"= "None", "2" = "Co-applicant", "3" = "Guarantor"))

gcc$Duration.in.Current.address<- as.factor(gcc$Duration.in.Current.address)
gcc$Duration.in.Current.address <- revalue(gcc$Duration.in.Current.address , c("1"= " <=1 year ", "2" = "1 to 2 years", "3" = "2 to 3 years","4" = " >4 years"))

gcc$Most.valuable.available.asset <- as.factor(gcc$Most.valuable.available.asset)
gcc$Most.valuable.available.asset <- revalue(gcc$Most.valuable.available.asset, c("1" = "Real-Estate", "2" = "Savings/Life Insurance", "3" = "Car/Other", "4" = "Unknown/No Property"))

gcc$Concurrent.Credits <- as.factor(gcc$Concurrent.Credits)
gcc$Concurrent.Credits <- revalue(gcc$Concurrent.Credits, c("1"= "Bank", "2" = "Stores", "3" = "None"))

gcc$Type.of.apartment <- as.factor(gcc$Type.of.apartment)
gcc$Type.of.apartment <- revalue(gcc$Type.of.apartment, c("1"= "Rent", "2" = "Own", "3" ="For Free"))

gcc$Occupation <- as.factor(gcc$Occupation)
gcc$Occupation <- revalue(gcc$Occupation, c("1" = "Unemployed/unskilled", "2" = "Unskilled-Resident", "3" = "Skilled employee/Official", "4" = "Management/self-employed/highly qualified employee/officer"))

gcc$Foreign.Worker <- as.factor(gcc$Foreign.Worker)
gcc$Foreign.Worker <- revalue(gcc$Foreign.Worker, c("1" = "Yes", "2" = "No"))

gcc$Telephone <- as.factor(gcc$Telephone)
gcc$Telephone <- revalue(gcc$Telephone, c("1" = "Yes", "2" = "No"))
```



#subset data into good and bad credit for post-hoc analysis
```{r}
Goodgcc <- subset(gcc, gcc$Creditability == 'Good')
Badgcc <- subset(gcc,gcc$Creditability == 'Bad')

```


# Write gcc cleaned data frame into .csv file
```{r}
write.csv(gcc,"Clean_Master.csv", row.names = FALSE)
```


# Seperate data in Good and Bad sets for weighting (if needed)
```{r}
write.csv(Goodgcc,"Clean_Master_Good.csv", row.names = FALSE)
write.csv(Badgcc,"Clean_Master_Bad.csv", row.names = FALSE)
```

